---
title: "ISLR Chapter 2"
author: "John Jacobi"
output: html_notebook
---

```{r}
library(tidyverse)
library(ISLR2)
```


## Question 1

### A

A flexible model will perform better.

### B

An inflexible model will perform better. A flexible model is likely to overfit on small amounts of data.

### C

A flexible model will perform better.

### D

An inflexible model will perform better.

## Question 2

### A

A regression model focused on inference. n = 500, p = 3

### B

A classification model focused on prediction. n = 20, p = 13

### C

A regression model focused on prediction. n = 52, p = 3

## Question 3

## Question 4

## Question 5

## Question 6

## Question 7

## Question 8

```{r}

## A
college <- read_csv('data/College.csv') %>% rename(School = "...1")

## B

# Skipped

## C

# i
summary(college %>% select(-School))

# ii
pairs(college %>% select(3:12))

# iii 
ggplot(data = college, aes(x = Private, y = Outstate)) +
  geom_boxplot() +
  theme_minimal()

# iv
college %>% 
  mutate(Elite = if_else(Top10perc > 50, "Yes", "No")) %>%
  ggplot(aes(x = Elite, y = Outstate)) +
  geom_boxplot() +
  theme_minimal()

# v
college %>%
  select(Top10perc, Room.Board, PhD, Grad.Rate) %>%
  pivot_longer(cols = 1:4) %>%
  ggplot(aes(x = value)) +
  geom_bar() +
  facet_wrap(~name, scales = "free") +
  theme_minimal()
```

## Question 9

```{r}
pairs(Auto)
```

## QUestion 10

```{r}
pairs(Boston)
```

```{r}
summary(Boston)
```

